---
title: "rcourse_lesson3_writeup"
author: "Nade Kang"
date: "June 9, 2018"
output: html_document
---

```{r, echo=FALSE}
load("rcourse_lesson3_environment.RData")
```

# Introduction

I analyzed the Giants' 2010 World Series winning season to see what could significantly predict games they won. I looked at both full season data (all 162 games) and games specific to when Buster Posey was playing.

# Results

## Full Season Data

For the full season data I tested for an effect of whether the Giants had more wins after the All-Star break or before the All-Star break. Initial visual examination of the data suggests that numerically they won a higher percentage of games after the All-Star break, but the effect looks very small.

```{r, echo=FALSE, fig.align='center'}
allstar.plot
```

To test this effect I ran a logistic regression with win or loss as the dependent variable and before or after the All-Star break as the independent variable. There was no significant effect of the All-Star break.

```{r}
allstar.glm_sum
```

## Buster Posey Data

We also examined Posey's data in similar way.

```{r, echo=FALSE, fig.align='center'}
posey_walked.plot
```

Here the estimated intercept is -0.09531, "no" is the default value, so if Posey was NOT walked, the Giants were below 50% for winning, although p-value tells this is not statistically significant the walked variable however, shows 2.49 quite positive with significant p-value, suggesting that if Posey walked, Giants were more likely to win.
```{r, echo=FALSE, fig.align='center'}
posey_walked.glm_sum
```
